---
title: "Untitled"
author: "Danuscha Große-Hering"
date: "17 7 2021"
output:
  pdf_document: default
---
```{r}
setwd("C:\\Users\\danus\\OneDrive\\Uni\\4.Semester\\Grundlagen der Versuchspalnung\\1.Experiment\\GdV-Experiment-1\\Experiment 3")
```

# Versuchsablauf

# Screening
```{r}

library(SixSigma)


ExperimentDesign  = expand.grid(A = c(-1, 1), B = c(-1,1), C = c(-1, 1), D = c(-1,1), E = c(-1,1) )
"F" = ExperimentDesign$A * ExperimentDesign$C * ExperimentDesign$D
G = ExperimentDesign$A * ExperimentDesign$B * ExperimentDesign$C



ExperimentDesign$F = F
ExperimentDesign$G = G

```

```{r}
Screening <- read.csv("Screening.CSV", sep = ";",dec = ",")
S <- Screening[order(Screening[,2]),]
S <-cbind(S, ExperimentDesign)
```

```{r}
summary(lm(Zeit.ohne.Klammer ~A+B+C+D+E+F+G, data= S))
```
```{r}
summary(lm(Zeit.mit.Klammer ~A+B+C+D+E+F+G, data= S))
```

# Optimierung
```{r}
Optimierung <-read.csv("Optimierung.CSV", sep = ";",dec = ",")

#erster Durchlauf
set.seed(1735)
p1 <-expand.grid(A = c(-1,0, 1),  G = c(-1,0,1) )
p1 <- cbind(1:9,p1)
#zweiter Durchlauf
set.seed(1736)
s <-sample(1:9,9)
p2 <-p1[s,]


p <- rbind(p1,p2)
names(p)[1] <- "Nr."
o1 <-cbind(Optimierung,p[1:9,2:3])

o2 <- o1[,-3]
o3 <- o1[,-2]

names(o2)[2] <- "Zeit"
names(o3)[2] <- "Zeit"

o <- rbind(o2,o3)
o$Asquare <- o$A^2
o$Gsquare <- o$G^2

lm(Zeit ~A + Asquare+G+Gsquare, data = o)
```


$\Rightarrow f(x_1,x_2)=3.47+00.44 \cdot x_1+0.06 \cdot x_1^2-0.67 \cdot x_2 + 0.29 \cdot x_2^2 \Rightarrow \frac{\partial{f}}{\partial{x}}= \begin{pmatrix}
0.44+0.12 \cdot x_1 \\
-0.67+0.58 \cdot x_2
\end{pmatrix}$
$\Rightarrow \frac{\partial{f}}{\partial{x}} = 0 \Rightarrow 0.44=-0.12 \cdot x_1 \land 0.67=0.58 \cdot x_2 \Rightarrow x_1 =-3.67 \land x_2=1.16$

$\Rightarrow \frac{\partial^2{f}}{\partial^2{x}}= 
\begin{pmatrix}
0.12    & 0 \\
0 & 0.58 
\end{pmatrix}$


```{r}
 det(matrix(c(0.12,0,0,0.58), ncol = 2))
```

$\Rightarrow \Rightarrow \frac{\partial^2{f}}{\partial^2{x}}$ ist positiv definit $\Rightarrow x=$ 
$\begin{pmatrix}
-3.67\\
1.16 
\end{pmatrix}$ 
 ist Maximum. 